---
title: "Assignment 4"
author: "Tianlang Yang"
date: "February 21, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##10.5

##1.
Tibbles are data frames, and only print a limited number of rows and show the class on top of each column.
```{r}

library(tidyverse)
mtcars
```

##2.
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]

tbl <- as_tibble(df)
tbl$x
tbl[, "xyz"]
tbl[, c("abc", "xyz")]

```


##3.
You can use the double bracket. You can't use the dollar sign, because df$var would look for a column named var.

##4.
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)

annoying[["1"]]
annoying$`1`
ggplot(annoying, aes(x = `1`, y = `2`)) +
  geom_point()
annoying[["3"]] <- annoying$`2` / annoying$`1`
annoying <- rename(annoying, one = `1`, two = `2`, three = `3`)
glimpse(annoying)
```

##5.
It converts named vectors to a data frame with names and values
```{r}
enframe(c(a = 1, b = 2, c = 3))

```

##6.
The print function for tibbles is in print.tbl_df
The option n_extra determines the number of extra columns to print information for.



##12.6.1
```{r}
who1 <- who %>%
  gather(new_sp_m014:newrel_f65, key = "key", value = "cases", na.rm = TRUE)
glimpse(who1)
who2 <- who1 %>%
 mutate(key = stringr::str_replace(key, "newrel", "new_rel"))
who3 <- who2 %>%
  separate(key, c("new", "type", "sexage"), sep = "_")
who3
who3 %>%
  count(new)
who4 <- who3 %>%
  select(-new, -iso2, -iso3)
who5 <- who4 %>%
  separate(sexage, c("sex", "age"), sep = 1)
who5

```

##1
It is okay to treat missing values the same, and we don't lose any information by dropping them.
```{r}
who1 %>%
  filter(cases == 0) %>%
  nrow()

gather(who, new_sp_m014:newrel_f65, key = "key", value = "cases") %>%
  group_by(country, year)  %>%
  mutate(missing = is.na(cases)) %>%
  select(country, year, missing) %>%
  distinct() %>%
  group_by(country, year) %>%
  filter(n() > 1)
```

##2
separate emits the warning "too few values", and if we check the rows for keys beginning with "newrel_", we see that sexage is messing, and type = m014
```{r}
who3a <- who1 %>%
  separate(key, c("new", "type", "sexage"), sep = "_")
filter(who3a, new == "newrel") %>% head()
```

##3
```{r}
select(who3, country, iso2, iso3) %>%
  distinct() %>%
  group_by(country) %>%
  filter(n() > 1)
```

```{r}
who5 %>%
  group_by(country, year, sex) %>%
  filter(year > 1995) %>%
  summarise(cases = sum(cases)) %>%
  unite(country_sex, country, sex, remove = FALSE) %>%
  ggplot(aes(x = year, y = cases, group = country_sex, colour = sex)) +
  geom_line()
```
