---
title: "Assignment 4"
author: "Tianlang Yang"
date: "February 21, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##10.5

##1.
Tibbles are data frames, and only print a limited number of rows and show the class on top of each column.
```{r}

library(tidyverse)
mtcars
```

##2.
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]

tbl <- as_tibble(df)
tbl$x
tbl[, "xyz"]
tbl[, c("abc", "xyz")]

```


##3.
You can use the double bracket. You can't use the dollar sign, because df$var would look for a column named var.

##4.
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)

annoying[["1"]]
annoying$`1`
ggplot(annoying, aes(x = `1`, y = `2`)) +
  geom_point()
annoying[["3"]] <- annoying$`2` / annoying$`1`
annoying <- rename(annoying, one = `1`, two = `2`, three = `3`)
glimpse(annoying)
```

##5.
It converts named vectors to a data frame with names and values
```{r}
enframe(c(a = 1, b = 2, c = 3))

```

##6.
The print function for tibbles is in print.tbl_df
The option n_extra determines the number of extra columns to print information for.