---
title: "Simple R Functions "
author: "Tianlang Yang"
date: "January 26, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1.

(a) Write functions \texttt{tmpFn1} and \texttt{tmpFn2} such that if \texttt{xVec} is the vector $(x_1, x_2, ... ,x_n)$, then \texttt{tmpFn1(xVec)} returns vector $(x_1, x_2^2, ..., x_n^n)$ and \texttt{tmpFn2(xVec)} returns the vector $(x_1, \frac{x_2^2}{2}, ..., \frac{x_n^n}{n})$.

******

Here is \texttt{tmpFn1}
```{r}

tmpFn1 <- function(xVec){
  return(xVec^(1:length(xVec)))
}

```

and now \texttt{tmpFn2}

```{r}
tmpFn2 <- function(xVec2){
  
  n = length(xVec2)
  
  return(xVec2^(1:n)/(1:n))
}

```

######  
  
  
  
(b) Now write a fuction \texttt{tmpFn3} which takes 2 arguments $x$ and $n$ where $x$ is a single number and $n$ is a strictly positive integer.  The function should return the value of   
$$1 + \frac{x}{1} + \frac{x^2}{2} + \frac{x^3}{3} + ... + \frac{x^n}{n}$$

```{r}
tmpFn3 <- function(x,n){
  
  N = 1:n
  
  return(1+sum(x^(N)/(N)))}


```

\newpage
### 2. Write a funciton \texttt{tmpFn(xVec)} such that if \texttt{xVec} is the vector $x = (x_1, ...,x_n)$ then \texttt{tmpFn(xVec)} returns the vector of moving averages:

$$\frac{x_1 + x_2 + x_3}{3}, \frac{x_2 + x_3 + x_4}{3}, ...,\frac{x_{n-2} + x_{n-1} + x_n}{3}$$

```{r}
tmpFn <- function(xVec){
  
  n = length(xVec)
  return((xVec[1:(n-2)]+xVec[2:(n-1)]+xVec[3:n])/3)}

tmpFn(c(1:10, 6:1))
```

Try out your function.  \texttt{tmpFn}(c(1:5,6:1))

### 3. Consider the continuous function

$$f(x) = \left\{\begin{matrix}
x^2 + 2x + 3 & if  & x < 0 \\ 
x + 3 & if & 0 \leq x < 2 \\ 
x^2 + 4x - 7 & if & 2 \leq  x 
\end{matrix}\right.$$

Write a function \texttt{tmpFn} which takes a single argument \texttt{xVec}.  the function should return the vector the values of the function $f(x)$ evaluated at the values in \texttt{xVec}.  
Hence plot the function $f(x)$ for $-3 < x <3$.

```{r}
tmpFn <- function(xVec){
  for(i in c(1:length(xVec))){
    varx <- xVec[i]
    if(varx<0){
      xVec[i] <- (varx^2)+(2*varx)+3
    }
    else if(varx>=0 && varx<2){
      xVec[i] <- varx+3
    }
    else{
      xVec[i] <- (varx^2)+(4*varx)-7
    }
  }
  return(xVec)
}

res <- tmpFn(seq(-3,3,by=0.1))
res
plot(seq(-3,3,by=0.1),res)
```


### 4. Write a function which takes a single argument which is a matrix.  The function should return a matrix which is the same as the function argument but every odd number is doubled.  
Hence the result of using the function on the matrix   

$$\begin{bmatrix}
1 & 1 & 3\\ 
5 & 2 & 6\\ 
-2 & -1 & -3
\end{bmatrix}$$

should be:

$$\begin{bmatrix}
2 & 2 & 6\\ 
10 & 2 & 6\\ 
-2 & -2 & -6
\end{bmatrix}$$

```{r}
tmpFn4 <- function(MatrixX){
  matrixXX <- apply(MatrixX, 1, function(x){ifelse(x%%2==0, x, x*2)})
  return(t(matrixXX))
}
```


### 5. Write a function which takes 2 arguements $n$ and $k$ which are positive integers.  It should return the $\mathit{n} x \mathit{n}$ matrix:


$$\begin{bmatrix}
k & 1 & 0 & 0 & \cdots  & 0 & 0\\ 
1 & k & 1 & 0 & \cdots  & 0 & 0\\
0 & 1 & k & 1 & \cdots  & 0 & 0\\
0 & 0 & 1 & k & \cdots  & 0 & 0\\
\cdot & \cdot & \cdot & \cdot & \cdot & \cdot & \cdot\\ 
0 & 0 & 0 & 0 & \cdots  & k & 1\\
0 & 0 & 0 & 0 & \cdots  & 1 & k
\end{bmatrix}$$

```{r}
tmpFn5 <- function(k,n){
  matE = diag(k,nrow =n, ncol=n)
  matE[abs(row(matE)-col(matE))==1] <- 1
  return(matE)
}
```


### 6. Suppose an angle $\alpha$ is given as a positive real number of degrees.  
If $0 \leq \alpha < 90$ then it is quadrant 1.  If $90 \leq \alpha < 180$ then it is quadrant 2.  
if $180 \leq \alpha < 270$ then it is quadrant3.  if $270 \leq \alpha < 360$ then it is quadrant 4.  
if $360 \leq \alpha < 450$ then it is quadrant 1.  
And so on ...   

Write a function \texttt{quadrant(alpha)} which returns the quadrant of the angle $\alpha$.

```{r}
quadrant <- function(alpha){
  module <- alpha%%360
  if(module>=0 && module<90){
  return(1)
}
  else if(module>=90 && module<180){
  return(2)
}
  else if(module>=180 && module<270){
  return(3)
}
  else{
  return(4)
}
}

```


### 7.

(a) Zeller's congruence is the formula:

$$ f = ([2.6m - 0.2] + k + y + [y/4] + [c/4] - 2c)mod 7 $$
where $[x]$ denotes the integer part of $x$; for example $[7.5] = 7$.  

Zeller's congruence returns the day of the week $f$ given:

$k$ = the day of the month  
$y$ = the year in the century  
$c$ = the first 2 digits of the year (the century number)  
$m$ = the month number (where January is month 11 of the preceding year, February is month 12 of the preceding year, March is month 1, etc.)   
For example, the date 21/07/1`963 has $m = 5, k = 21, c = 19, y = 63$;  
the date 21/2/63 has $m=12, k=21, c=19, and y=62$.  
Write a function \texttt{weekday(day,month,year)} which returns the day of the week when given the numerical inputs of the day, month and year.  
Note that the value of 1 for $f$ denotes Sunday, 2 denotes Monday, etc.

```{r}
weekday <- function(day,month,year){
  k <- day
  m <- (month+10)%%13
  y <- year%%100-1+(month+10)%/%12
  c <- year%/%100
  list_weekdays <- c("Saturday","Sunday","Monday","Tuesday",
  "Wednesday","Thursday","Friday")
  names(list_weekdays) = c(0:6)
  f <- (floor(2.6*m-0.2)+k+y+floor(y/4)+floor(c/4)-2*c)%%7
  print(f)
  return(list_weekdays[as.character(f)])
}
weekday(2,2,2018)

```

(b) Does your function work if the input parameters \text{day, month, and year} are vectors with the same length and valid entries?

#Yes. 
```{r}
weekday(c(2,4),c(2,2),c(2018,2018))

```









